\vskip-0.6in \Large Political Uncertainty

### 2015-12-31 GS-extension.tex
add notes on SOC for one non-neg bribe case and general conditions for SOCs

@@

		Solving for the determinant of this matrix:
		\[
		  (-1)\cdot 
			\left|\begin{array}{cccc}
				0 & 0 & 0 & -1\\
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
			\end{array} \right|
		\]
	\end{itemize}

>>>>

\vskip1in
In general
\begin{itemize}
	\item $n$ is the number of choice variables ($n=3$ in my case for the three bribes)
	\item If there are $k$ inequality constraints ($k=3$ in my case, for 3 non-negativity constraints)
	\item And $g_1$ through $g_b$ are binding (i.e. $b$ is the number of bribes that are zero)
	\item $m$ is the number of equality constraints (0 in my case)
	\item Then there are restrictions on the last ($n-b+m$) minors
		\begin{itemize}
			\item If one bribe is zero, then need the last two $3-1 =2$ minors to alternate in sign with the last being $(-1)^n = (-1)^3 = -1 <0$, i.e. negative
			\item If no bribes are zero, there are restrictions on the last three minors, but the matrix is 3x3 (no constraint rows)
			\item If two bribes are binding, there is only a restriction on the last minor, but it's a 5x5 matrix.
				\begin{itemize}
					\item But can't wipe out $\frac{1}{W_B}$ using two FOCs because only one holds with equality
				\end{itemize}
		\end{itemize}
	\item If all three non-negativity constraints bind, we know all bribes are zero. No restriction on SOC?
\end{itemize}

@@

		Solving for the determinant of this matrix:
		\[
		  (-1)\cdot 
			\left|\begin{array}{cccc}
				0 & 0 & 0 & -1\\
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
			\end{array} \right|
		=
						  (-1)\cdot (-1) \cdot (-1)
			\left|\begin{array}{ccc}
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2}\\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
			\end{array} \right| =
		\]
		\[
		  (-1) \cdot (-1)
			\left|\begin{array}{cc}	
			0 & \frac{\partial^2 L}{\partial b(0)^2}\\
			-1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
			\end{array} \right| = 0 - (-1) \cdot \frac{\partial^2 L}{\partial b(0)^2} = \frac{\partial^2 L}{\partial b(0)^2}
		\]
		\item Thus we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$
			\begin{itemize}
				\item This boils down to $\left(e^{-X} - 1\right) < 0$
				\item Implies $X > 0$
				\item i.e. $-\al + b(0) > 0$ or $b(0) > \al$
			\end{itemize}
		\item \textbf{Why does $b(0)$ have to be such that $X=Y$ even though $b\left(\frac{1}{2}\right) =0$?}
		\item Can write out SOC (just after equation 33) and FOC, sub together to get
			\[
			  \frac{1}{1 + e^{-X}} \left(e^{-Z} - 1\right) < 0
			\]
			Not sure what this means
	\end{itemize}
